Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-21 Document/paper.tex
edit

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{correlations_twisting_triaxiality_MHD.pdf}
\end{center}
\caption{Twisting in the halo-disc alignment (measured as the standard deviation
  of the alignment angles between two minor shape axis)
  as a function of the halo triaxialiy at the radius indicated
  in each panel's title.
  The label with the $\rho$ value corresponds to the Spearman's rank
  correlation coefficient while the line shows the result of the
  minimum squares fit to the data.
  Twisting does not correlate with triaxility in the same way at every
  radii. The strongest correlation appears around $0.12R_{200}\approx
  28\pm2$ kpc.} 
\label{fig:alignment_correlations}
\end{figure*}

@@

The lower row in Figure \ref{fig:cumulative_alignment} shows th
results for the MHD simulations.
The most striking feature of this plot is that around the radius of
$0.25R_{200}$ there is an almost perfect halo-disc alignment measured
in three shape axis.
Above and below this radius the degree of alignment changes.
We find the strongest missalignments at a radius of $0.06R_{200}$ when
the median and the standard deviation of the alignment angles between
the minor/median/major axis are $18\pm18$, $25\pm22$ and $7\pm21$
degrees, respectively;  at $0.25R_{200}$ these values drop to $2\pm3$,
$2\pm4$ an $1\pm 3$ degrees, respectively

@@

Figure \ref{fig:alignment_correlations} shows the correlation between
twisting at the four different radii at which we have measured the
alignments.

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{correlations_twisting_triaxiality_MHD.pdf}
\end{center}
\caption{Twisting in the halo-disc alignment (measured as the standard deviation
  of the alignment angles between two minor shape axis)
  as a function of the halo triaxialiy at the radius indicated
  in each panel's title.
  The label with the $\rho$ value corresponds to the Spearman's rank
  correlation coefficient while the line shows the result of the
  minimum squares fit to the data.
  Twisting does not correlate with triaxility in the same way at every
  radii. The strongest correlation appears around $0.12R_{200}$ ($28\pm2$ kpc).} 
\label{fig:alignment_correlations}
\end{figure*}

@@

The lower row in Figure \ref{fig:cumulative_alignment} shows th
results for the MHD simulations.
The most striking feature of this plot is that around the radius of
$0.25R_{200}$ there is an almost perfect halo-disc alignment measured
in three shape axis.
Above and below this radius the degree of alignment changes.
We find the strongest missalignments at a radius of $0.06R_{200}$ when
the median and the standard deviation of the alignment angles between
the minor/median/major axis are $18\pm18$, $25\pm22$ and $7\pm21$
degrees, respectively;  at $0.25R_{200}$ these values drop to $2\pm3$,
$2\pm4$ and $1\pm 3$ degrees, respectively

@@

Figure \ref{fig:alignment_correlations} shows the correlation between
twisting at the four different radii at which we have measured the
alignments. 
The median, mean vand standard deviation of the triaxiliy are $3$, $7$ and $8$
degrees, respectively.
The correlation between twisting and triaxility also changes with
radius as measured by the Spearman's rank correlation coefficient.
The largest correlation shows with the halo triaxility measured at
$0.12R_{200}$. 
The most important consequence of this changing degree in correlation
is that twisting cannot only be explained by large triaxiality values
and a possibly noisy determination of the shape axis.
